### 2022-07-31 manuscript.Rmd
Make HPC ready

# Specify directory paths
data_dir <- here("data")
files_dir <- here("manuscript_files")
output_dir <- here("output")

@@

# Re-run steps that take a long time to compute?
run <- list(
  eeg_processing = FALSE,
  mixed_models = FALSE
)

@@

  # Process EEG data
  res <- pipeline$group_pipeline(
    vhdr_files = vhdr_files,
    log_files = logs,
    output_dir = output_dir,
    report_dir = NULL,
    downsample_sfreq = 125,
    bad_channels = NULL,
    ocular_correction = "auto",
    highpass_freq = 0.1,
    lowpass_freq = 30,
    triggers = c(221, 222),
    epochs_tmin = -0.5,
    epochs_tmax = 1.5,
    baseline_tmin = -0.2,
    baseline_tmax = 0.0,
    reject_peak_to_peak = 200,
    components = list(
      "name" = list("P1", "N170", "N400"),
      "tmin" = list(0.1, 0.15, 0.4),
      "tmax" = list(0.15, 0.2, 0.7),
      "roi" = list(
        c("PO3", "PO4", "POz", "O1", "O2", "Oz"),
        c("P7", "P8", "PO7", "PO8", "PO9", "PO10"),
        c("C1", "C2", "Cz", "CP1", "CP2", "CPz")
      )
    ),
    average_by = c("phase/condition"),
    perform_tfr = TRUE,
    tfr_subtract_evoked = FALSE,
    tfr_freqs = seq(4, 40, by = 1.0),
    tfr_cycles = seq(2, 20, by = 0.5),
    tfr_baseline_tmin = -0.45,
    tfr_baseline_tmax = -0.05,
    tfr_baseline_mode = "percent",
    perm_contrasts = list(
      c("Pre-insight/Informed", "Pre-insight/Naive"),
      c("Insight/Informed", "Insight/Naive"),
      c("Post-insight/Informed", "Post-insight/Naive")
    ),
    perm_tmin = 0.0,
    perm_tmax = 1.0,
    n_jobs = 1
  )
}

>>>>

# Specify directory paths
data_dir <- here("data")
files_dir <- here("manuscript_files")
output_dir <- here("output")
report_dir <- here("output/qc_reports")

@@

# Re-run steps that take a long time to compute?
run <- list(
  eeg_processing = TRUE,
  mixed_models = TRUE
)

@@

  # Process EEG data
  res <- pipeline$group_pipeline(
    vhdr_files = vhdr_files,
    log_files = logs,
    output_dir = output_dir,
    epochs_dir = here(output_dir, "epochs"),
    report_dir = report_dir,
    downsample_sfreq = 125,
    bad_channels = NULL,
    ocular_correction = "auto",
    highpass_freq = 0.1,
    lowpass_freq = 30,
    triggers = c(221, 222),
    epochs_tmin = -0.5,
    epochs_tmax = 1.5,
    baseline_tmin = -0.2,
    baseline_tmax = 0.0,
    reject_peak_to_peak = 150,
    components = list(
      "name" = list("P1", "N170", "N400"),
      "tmin" = list(0.1, 0.15, 0.4),
      "tmax" = list(0.15, 0.2, 0.7),
      "roi" = list(
        c("PO3", "PO4", "POz", "O1", "O2", "Oz"),
        c("P7", "P8", "PO7", "PO8", "PO9", "PO10"),
        c("C1", "C2", "Cz", "CP1", "CP2", "CPz")
      )
    ),
    average_by = c("phase/condition"),
    perform_tfr = TRUE,
    tfr_subtract_evoked = FALSE,
    tfr_freqs = seq(4, 40, by = 1.0),
    tfr_cycles = seq(2, 20, by = 0.5),
    tfr_baseline_tmin = -0.45,
    tfr_baseline_tmax = -0.05,
    tfr_baseline_mode = "percent",
    perm_contrasts = list(
      c("Pre-insight/Informed", "Pre-insight/Naive"),
      c("Insight/Informed", "Insight/Naive"),
      c("Post-insight/Informed", "Post-insight/Naive")
    ),
    perm_tmin = 0.0,
    perm_tmax = 1.0,
    n_jobs = 1
  )
}
